---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ura

<!-- badges: start -->
[![R-CMD-check](https://github.com/bengoehring/ura/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bengoehring/ura/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`ura` provides a set of tools for calculating inter-rater reliability (IRR) statistics by rater, allowing for real-time monitoring of rater progress and accuracy. While far from the first package to provide users access to IRR diagnostics (e.g., [irr](https://cran.r-project.org/web/packages/irr/irr.pdf)), `ura` aims to help researchers and supervisors efficiently monitor the coding progress of their research assistants. Please refer to the [associated working paper](https://bengoehring.github.io/files/perspectives-paper.pdf) for additional information about effectively monitoring research assistants' progress. 

## Installation

`ura` is currently only available on GitHub. You can install it from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bengoehring/ura")
```

## Usage Examples

```{r example}
library(ura)
## basic example code
summary(cars)
```
